---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "100%"
)
```

# RegLesson

<!-- badges: start -->
<!-- badges: end -->

The summer before the second year of my master's degree, I identified two weaknesses in
my skills:
I didn't know enough about linear regression, and I had grown a bit too dependent on
`tidyverse` over base R. The solution was obvious: write a package implementing
linear regression from the ground up,
using only base R. Instead of relying on `lm`, I built a `LinRegProblem` class to
store a linear model and associated data. I extended this with functions designed to make
it easier to solve textbook problems. I don't need a profiler to know this approach is
a lot less efficient than R's built-in functions, but implementing it was a useful exercise.

You can create `LinRegProblem` objects like so:

```{r setup}
library(RegLesson)

X <- LinRegProblem(mtcars[, -1], mtcars$mpg)
```

This represents a regression of `mpg` on all other `mtcars` variables.

the `do_problems` function evaluates expressions in an environment and prints the results. Required, omitted arguments are replaced with their values in the environment. Now we can check whether the model passes the overall $F$ test and get Working-Hoteling confidence bands for the observations.

```{r}
do_problems(
    X,
    regression_relation(),
    Working_Hoteling(X_h = cbind(1, as.matrix(mtcars[, -1])))
)
```

This package contains functions for several diagnostic tests as well. Have fun!

## Installation

You can install the development version of RegLesson from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ryan-heslin/RegLesson")
```
